### 2025-03-06 paper-aadm.tex
Fix some problems

\documentclass[leqno]{aadmbook}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float} %package for figure and table placement 
%all necessary packages should be here

@@

\begin{document}
\shorttitle{Metagraph approach for construction of an (m, n)-regular bipartite graph with a given girth}

@@

\markboth{{\small\rm \hfill O.V. Arutyunov, V.A. Skorokhodov - header
\hfill}\hspace{-\textwidth}%
\underline{${{}_{}}_{}$\hspace{\textwidth}}}
{\underline{${{}_{}}_{}$\hspace{\textwidth}}\hspace{-\textwidth}%
{\small\rm \hfill Metagraph approach for construction of an (m, n)-regular bipartite graph with a given girth -header
\hfill}}

@@

{\large\bf  METAGRAPH APPROACH FOR CONSTRUCTION OF AN (M, N)-REGULAR BIPARTITE GRAPH WITH A GIVEN GIRTH
\rule{0mm}{6mm}\renewcommand{\thefootnote}{}%Enter at least one, but not more than 3 MSCs.
% First entered MSC will be a primary one, others (at most 2) will be secondary.
\footnotetext{\scriptsize ${}^{\ast}$Corresponding author. John Doe}
\footnotetext{\scriptsize 2020 Mathematics Subject Classification. FILL SUBJECT MSCs HERE.

\rule{2.4mm}{0mm}Keywords and Phrases. Fill Keywords and Phrases Here - at most 5, separated by commas.}}

@@

% 11
\bibitem{algebraic_aproach_to_sc_ldpc}
Beemer, A., Habib, S., Kelley, C. A., & Kliewer, J. (2017). A generalized algebraic approach to optimizing SC-LDPC codes. In 55th Annual Allerton Conference on Communication, Control, and Computing, Allerton 2017 (pp. 672-679). (55th Annual Allerton Conference on Communication, Control, and Computing, Allerton 2017; Vol. 2018-January). Institute of Electrical and Electronics Engineers Inc. doi:10.1109/ALLERTON.2017.8262802

@@

>>>>

\documentclass[leqno]{aadmbook}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsmath, amsthm, amsfonts, amssymb}
\usepackage{float} %package for figure and table placement 
%all necessary packages should be here

@@

@@

\markboth{{\small\rm \hfill O.V. Arutyunov, V.A. Skorokhodov - header
\hfill}\hspace{-\textwidth}%
\underline{${{}_{}}_{}$\hspace{\textwidth}}}
{\underline{${{}_{}}_{}$\hspace{\textwidth}}\hspace{-\textwidth}%
{\small\rm \hfill Metagraph approach for construction of an (m, n)-regular bipartite graph with a given girth
\hfill}}

@@

{\large\bf  METAGRAPH APPROACH FOR CONSTRUCTION OF AN (M, N)-REGULAR BIPARTITE GRAPH WITH A GIVEN GIRTH
\rule{0mm}{6mm}\renewcommand{\thefootnote}{}%Enter at least one, but not more than 3 MSCs.
% First entered MSC will be a primary one, others (at most 2) will be secondary.

\footnotetext{\scriptsize ${}^{\ast}$Corresponding author. Oleg Arutyunov}
\footnotetext{\scriptsize 2020 Mathematics Subject Classification. 05C38, 05C90, 94B15.

\rule{2.4mm}{0mm} Keywords and Phrases. Bipartite graphs, girth, metagraphs, construction of graphs, regular graphs.}}

@@

% 11
\bibitem{algebraic_aproach_to_sc_ldpc}
Beemer, A., Habib, S., Kelley, C. A., Kliewer, J. (2017). A generalized algebraic approach to optimizing SC-LDPC codes. In 55th Annual Allerton Conference on Communication, Control, and Computing, Allerton 2017 (pp. 672-679). (55th Annual Allerton Conference on Communication, Control, and Computing, Allerton 2017; Vol. 2018-January). Institute of Electrical and Electronics Engineers Inc. doi:10.1109/ALLERTON.2017.8262802

@@

\end{thebibliography}

\vspace{1cc}

\noindent
{\bf Oleg V. Arutyunov}\\
Institute of Mathematics, Mechanics and Computer Science,\\
Southern Federal University,\\
Rostov-on-Don, Russia\\
E-mail: {\it ArutunoffOleg@yandex.ru}

\vspace{0.1cc}

\noindent
{\bf Vladimir A. Skorokhodov}\\
Institute of Mathematics, Mechanics and Computer Science,\\
Southern Federal University,\\
Rostov-on-Don, Russia\\
E-mail: {\it vaskorohodov@sfedu,ru}
